noam_data_exploration_v1

### 2024-07-23 noam_data_exploration_v3.Rmd
Found slight differences in how codyn calculates stability, so using that for the overall diversity stability dataframe. I still prefer CV.

diversity_stability_quadrat <- alpha_diversity_quad_sub %>%
  dplyr::group_by(Location, Site, Habitat, Site_habitat, Transect, Stratum) %>%
  dplyr::summarise(Richness_mean = mean(Richness), 
            Richness_se = sd(Richness)/sqrt(n()),
            Richness_cv = CV(Richness),
            Shannon_mean = mean(Shannon), 
            Shannon_se = sd(Shannon)/sqrt(n()),
            Shannon_cv = CV(Shannon),
            Shannon_stability = 1/CV(Shannon), # Stability as defined by codyn and many others (including Pete in 2022 paper)
            Cover_mean = mean(Cover),
            Cover_se = sd(Cover)/sqrt(n()),
            Cover_cv = CV(Cover),
            Cover_stability = 1/CV(Cover)) # as above

diversity_stability_quadrat <- 
  merge(diversity_stability_quadrat, lm_synchrony_quadrat, by = "Location") # add in loreau and de Mazancourt synchrony
diversity_stability_quadrat <- merge(diversity_stability_quadrat, gross_synchrony_quadrat, by = "Location")
diversity_stability_quadrat <- merge(diversity_stability_quadrat, quadrat_level_portfolio, by = "Location") # add in portfolio effects
diversity_stability_quadrat <- merge(diversity_stability_quadrat, variance_ratio_quadrat, by = "Location")
pairs(~ Cover_mean + Cover_cv + Cover_stability + 
        Shannon_mean + Shannon_cv + Shannon_stability + 
        Loreau_synchrony +  Portfolio_effect + VR, data = diversity_stability_quadrat)

>>>>

community_stability_quadrat <- community_stability(df = long_data_sub,
                                   time.var = "Year",
                                   abundance.var = "Percent_cover",
                                   replicate.var = "Location")
colnames(community_stability_quadrat) = c("Location", "Cover_stability")

diversity_stability_quadrat <- alpha_diversity_quad_sub %>%
  dplyr::group_by(Location, Site, Habitat, Site_habitat, Transect, Stratum) %>%
  dplyr::summarise(Richness_mean = mean(Richness), 
            Richness_se = sd(Richness)/sqrt(n()),
            Richness_cv = CV(Richness),
            Shannon_mean = mean(Shannon), 
            Shannon_se = sd(Shannon)/sqrt(n()),
            Shannon_cv = CV(Shannon),
            Shannon_stability = 1/CV(Shannon), # Stability as defined by codyn and many others (including Pete in 2022 paper)
            Cover_mean = mean(Cover),
            Cover_se = sd(Cover)/sqrt(n()),
            Cover_cv = CV(Cover))

diversity_stability_quadrat <- 
  merge(diversity_stability_quadrat, lm_synchrony_quadrat, by = "Location") # add in loreau and de Mazancourt synchrony
diversity_stability_quadrat <- merge(diversity_stability_quadrat, gross_synchrony_quadrat, by = "Location")
diversity_stability_quadrat <- merge(diversity_stability_quadrat, quadrat_level_portfolio, by = "Location") # add in portfolio effects
diversity_stability_quadrat <- merge(diversity_stability_quadrat, variance_ratio_quadrat, by = "Location")
diversity_stability_quadrat <- merge(diversity_stability_quadrat, community_stability_quadrat, by = "Location")
pairs(~ Cover_mean + Cover_cv + Cover_stability + 
        Shannon_mean + Shannon_cv + Shannon_stability + 
        Loreau_synchrony +  Portfolio_effect + VR, data = diversity_stability_quadrat)
